\section{Experience}
\detailsection{Software Engineer}{TI\&M AG}{https://ti8m.ch}{11/2021 - Present}
\begin{itemize}
    \item Engaged with clients, including the Swiss Parliament and a large Swiss bank, to identify specific needs and deliver tailored software solutions.
    \item Served on the Azure Cloud team, focusing on cloud services and infrastructure.
    \item Collaborated in large Agile/SCRUM development teams, refining user stories, estimating effort, and planning sprints.
    \item Built CI/CD pipelines to automate the deployment of software solutions and expedite the development process.
    \item Contributed to various phases of the software development lifecycle, from development to testing and deployment.
\end{itemize}
\subsection*{Projects}
\customparagraph{Pension Fund Web Application for a Large Swiss Bank}
\begin{itemize}
    \item Backend development using C\# .NET, aswell as Angular frontend development.
    \item Implemented CI/CD in GitLab and wrote Powershell scripts for running automated tests.
    \item Performance testing using K6, enabled us to identify and fix performance issues early on.
\end{itemize}
\dottedline
\customparagraph{Digital Platform for the Swiss Parliament}
\begin{itemize}
    \item Collaborated within a large Agile/SCRUM team using JIRA, Confluence, Gitflow, and SCRUM ceremonies.
    \item Java backend development and API design, database modelling using OpenAPI, Liferay, Hibernate, and SQL-Server.
\end{itemize}
\dottedline
\customparagraph{Active Directory Synchronization Using Azure Functions in C\#}
\begin{itemize}
    \item Developed GitLab pipelines using Terraform.
    \item Accessed Active Directory using GraphQL.
    \item Wrote Azure Functions and used Azure Service Bus in C\#, both created using Terraform.
\end{itemize}

\dottedline
\detailsection{3D Artist}{NOMOKO AG}{https://nomoko.world}{09/2018 - 07/2021}
\begin{itemize}
    \item Processed 3D data from drone-captured imagery.
    \item Created automation scripts to simplify the processing of large data sets.
    \item Worked on improving the quality of 3D data reconstruction.
    \item Created an in-house Python library using the Blender API to automate 3D data processing.
\end{itemize}
