\section{Experience}
\detailsection{Cloud Engineer}{SWICA}{https://www.swica.ch}{11/2023 - Present}
\begin{itemize}
    \item Building the container platform based on AKS.
    \item Assisting with the migration of on-premise workloads to the container platform.
\end{itemize}
\dottedline

\detailsection{Software Engineer}{TI\&M AG}{https://ti8m.ch}{11/2021 - Present}
\begin{itemize}
    \item Engaged with clients, including the Swiss Parliament and a large Swiss bank, to identify specific needs and deliver tailored software solutions.
    \item Served on the Azure Cloud team, focusing on cloud services and infrastructure.
    \item Collaborated in large Agile/SCRUM development teams, refining user stories, estimating effort, and planning sprints.
    \item Built CI/CD pipelines to automate the deployment of software solutions and expedite the development process.
    \item Contributed to various phases of the software development lifecycle, from development to testing and deployment.
\end{itemize}
\subsection*{Projects}
\customparagraph{Pension Fund Web Application for a Large Swiss Bank}
\begin{itemize}
    \item Backend development using C\# .NET, aswell as Angular frontend development.
    \item Implemented CI/CD in GitLab and wrote Powershell scripts for running automated tests.
    \item Performance testing using K6, enabled us to identify and fix performance issues early on.
\end{itemize}
\dottedline

\customparagraph{Digital Platform for the Swiss Parliament}
\begin{itemize}
    \item Collaborated within a large Agile/SCRUM team using JIRA, Confluence, Gitflow, and SCRUM ceremonies.
    \item Java backend development and API design, database modelling using OpenAPI, Liferay, Hibernate, and SQL-Server.
\end{itemize}
\dottedline

\customparagraph{Active Directory Synchronization Using Azure Functions in C\#}
\begin{itemize}
    \item Developed GitLab pipelines using Terraform.
    \item Accessed Active Directory using GraphQL.
    \item Wrote Azure Functions and used Azure Service Bus in C\#, both created using Terraform.
\end{itemize}
